---
title: "Data 607 Lab 3"
author: "Laura Choi"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Normalization

**Dataframe 1- Patient list with ID # and health insurance**

```{r patient_list}
patient_list <- data.frame(
  patient_ID = c( 1, 2, 3, 4, 5),
  last_name = c("Jones", "Green", "Murphy", "Brown", "Davis"),
  health_ins = c("Aetna", "Aetna", "Cigna", "BCBS", "EmblemHealth"),
  stringsAsFactors = FALSE
)
print(patient_list)
```
**Dataframe 2- Provider information with provider ID, and specialty** 

``` {r provider_info}
provider_info <- data.frame(
  provider_ID = c(12, 13, 14, 15),
  provider_lastname = c("Keller", "Johnson", "Stuart", "Williams"),
  provider_specialty = c("PCP", "OBGYN", "PED", "Internalist"),
  provider_credential = c("MD", "MD", "MD", "NP"),
  stringsAsFactors = FALSE
)
print(provider_info)
```

**Dataframe 3- Primary provider of patients listed in dataframe 1**

``` {r primary_provider}
primary_provider <- data.frame(
  patient_ID = c( 1, 2, 3, 4, 5),
  provider_ID = c(1, 2, 2, 3, 4),
  stringsAsFactors = FALSE
)
print(primary_provider)
```


# Character Manipulation

``` {r read data}
major_data <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/refs/heads/master/college-majors/majors-list.csv")
```

``` {r major data filtered}

major_datastat <- major_data[grep("DATA|STATISTICS", major_data$Major, ignore.case = TRUE), ]

major_datastat

```

# Describe in words, what these expressions will match

**(.)\1\1** : 

"(.)" signifies a single expression. "\1" signifies matching the expression. Together, "(.)\1\1" signifies a single expression, matching that single expression two times. 

For example: **"xxx"**, or **"yyy"**



**(.)(.)\\2\\1** :

As mentioned previously, "(.)" signifies a single or primary expression. The succeeding "(.)" signifies an additional secondary expression. "\\2" signifies a match for the secondary expression, while the "\\1" signifies matching the primary expression.

For example: **"xyyx"**, with x being the primary expression and y being the secondary expression. 


**(..)\1** : 

The "(..)" character signifies any two expressions and puts them in a singular group. As mentioned previously, the "\1" character matches the single expression. This would ultimately give us the following results. 

For example: **"xyxy"**


**(.).\\1.\\1**

From these characters, we will receive a five expression string. However, we must note that within the five expression string, the first, third, and fifth characters will all be the same. 

For example: **"xyxyx"** (Note that the first, third, and fifth characters are all "x".)



**(.)(.)(.).*\\3\\2\\1**

From these characters, we can assume from earlier that the three "(.)" listed are three expressions. The asterisk ".*" indicates that any number of characters can appear within the three "(.)" expressions and the remaining chunk. As previously mentioned, we know that the "\\1" and "\\2" expressions signify the primary and secondary expression respectively. The "\\3" signifies the third expression captured. Ultimately, we should receive the following outputs:

For example: **xyzHellozyx**

Another example: **abcgoodmorningcba**

# Construct regular expressions to match words that:

**Start and end with the same character.**
(.)\1

**Contain a repeated pair of letters**
(..)\1

**Contain one letter repeated in at least three places**
(.).\\1.\\1



